### 2014-06-04 ApTranscriptome_TR.Rmd

# add background list to DAVID
david.list <- addList(david.connect, refseq.id,
                      idType = "REFSEQ_PROTEIN",
                      listName = "ApTranscriptome_Amellifera_Drosophila_refseq_protein",
                      listType = "Background")
```

@@

# add genelist to DAVID
david.list <- addList(david.connect, A22.high.geneList.refseq.id,
                      idType = "REFSEQ_PROTEIN",
                      listName = "ApTranscriptome_A22_high",
                      listType = "Gene")

@@

# gbtain Functional Annotation Cluster
A22.high.termCluster <- getClusterReport(david.connect, type = "Term")
head(summary(A22.high.termCluster))
members(A22.high.termCluster)
plot2D(A22.high.termCluster, 1)
```

>>>>

# add background list to DAVID
david.background <- addList(david.connect, refseq.id,
                      idType = "REFSEQ_PROTEIN",
                      listName = "ApTranscriptome_Amellifera_Drosophila_refseq_protein",
                      listType = "Background")
```

@@

# add genelist to DAVID
david.geneList <- addList(david.connect, A22.high.geneList.refseq.id,
                      idType = "REFSEQ_PROTEIN",
                      listName = "ApTranscriptome_A22_high",
                      listType = "Gene")

@@

# obtain Functional Annotation Cluster
A22.high.termCluster <- getClusterReport(david.connect, type = "Term")
head(summary(A22.high.termCluster))
members(A22.high.termCluster)[[1]]$Term
members(A22.high.termCluster)[[2]]$Term
members(A22.high.termCluster)[[3]]$Term

plot2D(A22.high.termCluster, 3)
```
